Evolution of ORM Systems: Formal Foundations

### 2013-01-17 doc/description.tex
defined mapping from application to database

>>>>

\paragraph{Mapping of Application} The goal of ORM is usually to determine how an instance is stored in the database. The ORM maps the structure of application classes to database schema. The assumption is a software is evolved continuously and evolutionary transformations produces consistent software, nevertheless to verify consistency of a software we need mapping between an existing application structure and database schema. 
\begin{align*}
	\mathbf{\rho_{app}} : Application \rightarrow Database\\
	\rho_{app}(a) = \inference{state(a) = Consistent a}{\begin{gathered}
	db(\varnothing) \bullet addTable(classes(a)) \\ 
	\bullet (\forall c \in classes(a), p \in properties(c) : addProperty(name(c), p) \\
	\bullet (\forall c \in classes(a), e \in associations(c) : addAssociaiton(name(c), e) 
\end{gathered}}
\end{align*}
